Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-08-22 paper/paper.Rmd
ehermann + add all plots

```{r, fig.height=9, fig.width=6}
# library(png)
# layout(matrix(1:24,nr=6,byr=T))
# for (key in project_plan$project_key) {
#   orig <- readPNG(paste0("../figures/",key,"-original.png"))
#   rep <- readPNG(paste0("../figures/",key,"-replication.png"))
# 
#   par(mai=c(0,0,0,0))
#   plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
#   rasterImage(orig, 0, 0, 100, 100, interpolate=FALSE)
# 
#   plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
#   rasterImage(rep, 0, 0, 100, 100, interpolate=FALSE)
# 
# }
```

>>>>

```{r, fig.height=9, fig.width=6}
library(png)
layout(matrix(1:24,nr=6,byr=T))
for (key in project_plan$project_key) {
  orig <- readPNG(paste0("../figures/",key,"-original.png"))
  rep <- readPNG(paste0("../figures/",key,"-replication.png"))

  par(mai=c(0,0,0,0))
  plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
  rasterImage(orig, 0, 0, 100, 100, interpolate=FALSE)

  plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
  rasterImage(rep, 0, 0, 100, 100, interpolate=FALSE)

}
```
